---
title: "Random Forest Test"
author: "Chris Lewis"
date: "3/9/2017"
output: html_document
---

```{r}
library(randomForest)
library(hybridEnsemble)
library(caret)
library(caretEnsemble)
library(mlbench)


iris
dim(iris)

iris_data = data.frame(iris[-5])
iris_data


set.seed(100)
sample_data = sample(150, 100)

train_data = iris[sample_data, ]
train_data

test_data = iris[-sample_data, ]

rf_model = randomForest(Species ~., train_data, mtry = 2, ntree = 500)
rf_model




predict_model = predict(rf_model, test_data)
predict_model

predict_show=predict(rf_model, newdata=data.frame(Sepal.Length=5,Sepal.Width=3,Petal.Length=1.5,Petal.Width=.2), type='prob')

predict_show


table(test_data[,5], predict_model)

mean(test_data[,5] == predict_model)

importance(rf_model, type = 1)
varImpPlot(rf_model)

best_mtry = tuneRF(train_data, train_data$Species, ntreeTry = 500, stepFactor = 1.2, improve = .01, trace = T, plot = T)
best_mtry

```
###########################


set.seed(100)
control = trainControl(method = "repeatedcv", number=10, repeats=3)
stackControl = trainControl(method="repeatedcv", number=10, repeats=3, savePredictions = TRUE, classProbs = TRUE)
metric = "Accuracy"
fit.rf = train(Species~., data=iris, method = "rf", metric=metric, trControl=control )
fit.rf


algorithmList = c('lda', 'rpart', 'knn', 'svmRadial')
models = caretList(Species~., data=iris, trControl = stackControl, methodList = algorithmList)
stack.rf = caretStack(models, method="rf", metric="Accuracy", trControl=stackControl)
print(stack.rf)




unique(iris$Species)
iris$Species = ifelse(iris$Species == "setosa", 0)
iris$Species = ifelse(iris$Species == "veriscolor", 0.5)
iris$Species = ifelse(iris$Species == "virginica" , 1)




hybEns = hybridEnsemble(x=iris,y= iris$Species)



```{r}
library(randomForest)
library(hybridEnsemble)
library(caret)
library(RCurl)


iris



```










